---
title: "Tidytuesday:  March 10 2022"
format:
  html:
    theme: default
---

```{r, libraries}
library(ggrepel)
library(ggpubr)
library(tidytuesdayR)
library(tidyverse)
```
# Data

The data is saved in two objects `nyt_titles` and `nyt_full`.
The objects are a list of the NY Times Best Seller from 1931-2020. 
`nyt_titles` group the information by book and provide information about book's rank

```{r, data}

nyt_titles <- readr::read_tsv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-05-10/nyt_titles.tsv')
nyt_full <- readr::read_tsv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-05-10/nyt_full.tsv')

```

A first view of my objects:

```{r, inf}

list(nyt_full, nyt_titles)%>%
  map(head)
```
[//]: # "What can I use?"

# Who has been on the NY Times Best Seller list more times?

```{r, Discovering}

Counting<-nyt_titles%>%
  group_by(author)%>%
  summarize(Times=n())%>%
  arrange(desc(Times))

head(Counting)
```
Danielle Steel is the author with the most works on the NY Times Best Seller list. 
I am going to take a trip through his work to discover her stories.

```{r, Danielle}
library(lubridate)
Danielle_Steel<-nyt_titles%>%
  filter(author=="Danielle Steel")%>%
  mutate(year=ymd(Danielle_Steel$year, truncated = 2L))
```
[//]: # "How many books per year did she write??"

The first time she appeared in NY Times Best Seller list was in 1980, after that she always has been part of the NY Times best seller list.

```{r, Book_year}

P1<-Danielle_Steel%>%
  group_by(year)%>%
  summarize(Book_year=n())%>%
  ggplot(., aes(x=year, y=Book_year))+
  geom_line()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), 
        legend.position = "bottom",
        legend.title = element_blank(),
        plot.title = element_text(size = 10, face = "bold"))+
  labs(x = "Year", y="Number of books")+  
  scale_x_date(breaks = seq(min(Danielle_Steel$year), 
                            max(Danielle_Steel$year), by = "36 month"), date_labels = "%Y", expand = c(0, 0))+
  theme_minimal()+
    ggtitle("Books on the NY time Best Seller list written by Danielle Steel")

```
[//]: # "How many books have been 'the number One'??"

Since 1980, 35 of her books have ranked #1.

```{r, Number_One}

P2<-Danielle_Steel%>%
  filter(best_rank==1)%>%
  arrange(desc(total_weeks))%>%
  ggplot(., aes(x=year, y=total_weeks, label=title ))+
  geom_point(aes(color=year), show.legend = FALSE)+ 
  scale_color_gradient(low = "blue", high = "red")+
  geom_text_repel(aes(label = title),
                  box.padding   = 0.5, 
                  point.padding = 0.1,
                  segment.color = 'grey50')+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), 
        legend.position = "none",
        legend.title = element_blank(),
        plot.title = element_text(size = 10, face = "bold"))+
  labs(x = "Year", y="Number of weeks on the list")+  
  scale_x_date(breaks = seq(min(Danielle_Steel$year), 
                            max(Danielle_Steel$year), by = "36 month"), date_labels = "%Y")+
  theme_minimal()

```


```{r, fINAL}
title <- expression(scriptstyle("Kelly, Nicholas; White, Nicole, Glass, Loren, 03/01/2021, “The Program Era Project,” Post45 Data Collective, V1."))
Final<-annotate_figure(
  ggarrange(P1, P2, ncol=1),
  bottom = text_grob(title) ,
  fig.lab.pos = "bottom.left"
)

ggsave("Final.png")
```
